Global code motion of congruent instructions

### 2017-11-06 cgo/paper.tex
ssapre

\begin{figure}[h!]
  \includegraphics[width=0.4\textwidth]{chi-example.pdf}
  \vspace*{-1.0cm}
\caption{I1, I2 are instructions in B, and C respectively, CHIArg1 = \{V, B, I1\} and CHIArg2 = \{V, C, I2\}}
\label{fig:chi-intro}
\end{figure}

@@

\begin{verbatim}
struct CHIArg {
  // Edge destination (shows the direction of flow), may not be where the I is.
  BasicBlock *Dest;
  // The instruction which uses the values flowing out of CHI.
  Instruction *I;
  // The global value number of I.
  GVNType VN;
};

@@

Essentially, CHIArg1 = {V, B, I1} and CHIArg2 = {V, C, I2}

For sinking we use the similar approach as \ref{SSAPRE} to track values flowing
into a basic block.

>>>>

\begin{figure}[h!]
  \includegraphics[width=0.4\textwidth]{chi-example.pdf}
  \vspace*{-1.0cm}
\caption{I1, I2 are instructions in B, and C respectively, CHIArg1 = \{V, B,
  I1\} and CHIArg2 = \{V, C, I2\}, V is the value number for both I1, and I2}
\label{fig:chi-intro}
\end{figure}

@@

\begin{verbatim}
struct CHIArg {
  // Edge destination (shows the direction of flow),
  // may not be where the I is.
  BasicBlock *Dest;
  // The instruction CHI-arg refers to.
  Instruction *I;
  // The global value number of I.
  GVNType VN;
};

@@

Essentially, CHIArg1 = \{V, B, I1\} and CHIArg2 = \{V, C, I2\}

For sinking we use the similar approach as \cite{ssapre} to track values flowing
into a basic block.
